Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-16 WSSSPE4_report/WSSSPE4_report.tex
added description of metrics lightning talk

    \item \textbf{Gabrielle Allen, Emily Chen\textsuperscript{\textasteriskcentered},
    Ray Idaszak, and Daniel S.\ Katz: \textit{Report on Software Metrics for
    Research Software}}~\cite{GAllen:2016wsb}.
    \note{Description}

>>>>

    \item \textbf{Gabrielle Allen, Emily Chen\textsuperscript{\textasteriskcentered},
    Ray Idaszak, and Daniel S.\ Katz: \textit{Report on Software Metrics for
    Research Software}}~\cite{GAllen:2016wsb}.
    In this talk, Chen first summarized some of the outcomes of the WSSSPE3
    Metrics Breakout Group, who discussed that metrics are important for scientific
    impact, discovery, reducing duplication of efforts, and evaluating software.
    The group also summarized barriers to widespread use of metrics: no common
    set of metrics collected, a need for usefulness to be obvious for projects,
    and no common standard for collecting\slash presenting metrics. To find out
    more about practices related to metrics, the authors ran a survey of National
    Science Foundation Software Infrastructure for Sustained Innovation (SI2)
    program investigators, with 19 participants. Important results include the
    observation that most use citations and acknowledgements of software in
    funding proposals, while download numbers are both challenging to collect
    and not useful. Overall, participants generally agreed that metrics are
    important, but said useful metrics are difficult or tedious to collect.
